Combining global tree cover loss data with historical national forest cover maps to look at six decades of deforestation and forest fragmentation in Madagascar

### 2018-01-18 manuscript/manuscript.Rnw
Update gitignore
Update and numbering bibliography section

\documentclass[a4paper, 12pt, leqno]{article} %leqno: numéro d'équation à gauche
\pagenumbering{arabic} % choose how to number the pages
\usepackage{a4wide}
\usepackage[utf8]{inputenc} % accents interprétés
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage[hmargin=2cm, vmargin = 2cm, noheadfoot]{geometry} %% Pour gérer le format des pages
%\usepackage{layout} %% Pour avoir la longueur des marges
\usepackage[round,sort]{natbib} %% Natbib is a popular style for formatting references.
%\usepackage{multibib}
%\newcites{secnm}{Bibliographie} 
%\usepackage{verbatim} % for multiline comments
\usepackage{amssymb} %symbole de maths
\usepackage{amsmath} %idem
%\usepackage{stmaryrd} %% Symbole flèche à l'envers
%\usepackage{amsfonts}
\usepackage[english]{babel} %% Les titres en anglais
\usepackage{array} %% Pour centrer verticalement le contenu d'un tableau, entre autres...
\setcounter{secnumdepth}{4} %% Profondeur des sections, subsections
\usepackage{setspace} %% Gère l'interligne: singlespacing, doublespacing
\usepackage{booktabs}
%\singlespacing
\usepackage{longtable}
\usepackage[table]{xcolor}
\setlength{\LTleft}{-5cm plus 1 fill}
\setlength{\LTright}{-5cm plus 1 fill}
\usepackage[colorlinks=true,citecolor=blue]{hyperref} %% Gère les hyperliens
\usepackage{lineno} %% Numérotation des lignes
%\linenumbers
\newcommand{\logit}{\text{logit}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\p}{\text{p}}
\newcommand{\R}{\textnormal{\sffamily\bfseries R}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

@@

\title{Combining global tree cover loss data with historical national
  forest cover maps to look at six decades of deforestation and forest
  fragmentation in Madagascar}
\date{}

@@

%%\bibliographystyle{besjournals}
%%\bibliography{biblio}

\begin{thebibliography}{60}
\providecommand{\natexlab}[1]{#1}

\bibitem[{Achard \emph{et~al.}(2014)Achard, Beuchle, Mayaux, Stibig, Bodart,
  Brink, Carboni, Desclée, Donnay, Eva, Lupi, Raši, Seliger \&
  Simonetti}]{Achard2014}
Achard, F., Beuchle, R., Mayaux, P., Stibig, H.J., Bodart, C., Brink, A.,
  Carboni, S., Desclée, B., Donnay, F., Eva, H.D., Lupi, A., Raši, R.,
  Seliger, R. \& Simonetti, D. (2014) Determination of tropical deforestation
  rates and related carbon losses from 1990 to 2010. \emph{Global Change
  Biology} \textbf{20}, 2540--2554.

\bibitem[{Aleman \emph{et~al.}(2017)Aleman, Jarzyna \& Staver}]{Aleman2017}
Aleman, J.C., Jarzyna, M.A. \& Staver, A.C. (2017) Forest extent and
  deforestation in tropical africa since 1900. \emph{Nature Ecology \&
  Evolution} .

\bibitem[{Ali \& Aitchison(2008)}]{Ali2008}
Ali, J.R. \& Aitchison, J.C. (2008) {Gondwana to Asia: Plate tectonics,
  paleogeography and the biological connectivity of the Indian sub-continent
  from the Middle Jurassic through latest Eocene (166--35 Ma)}.
  \emph{Earth-Science Reviews} \textbf{88}, 145--166.

\bibitem[{Allnutt \emph{et~al.}(2008)Allnutt, Ferrier, Manion, Powell,
  Ricketts, Fisher, Harper, Irwin, Kremen, Labat, Lees, Pearce \&
  Rakotondrainibe}]{Allnutt2008}
Allnutt, T.F., Ferrier, S., Manion, G., Powell, G.V.N., Ricketts, T.H., Fisher,
  B.L., Harper, G.J., Irwin, M.E., Kremen, C., Labat, J.N., Lees, D.C., Pearce,
  T.A. \& Rakotondrainibe, F. (2008) {A method for quantifying biodiversity
  loss and its application to a 50-year record of deforestation across
  Madagascar}. \emph{Conservation Letters} \textbf{1}, 173--181.

\bibitem[{Armitage \emph{et~al.}(2015)Armitage, Highfield, Brody \&
  Louchouarn}]{Armitage2015}
Armitage, A.R., Highfield, W.E., Brody, S.D. \& Louchouarn, P. (2015) {The
  contribution of mangrove expansion to salt marsh loss on the Texas Gulf
  Coast}. \emph{PloS One} \textbf{10}, e0125404.

\bibitem[{Bastin \emph{et~al.}(2017)Bastin, Berrahmouni, Grainger, Maniatis,
  Mollicone, Moore, Patriarca, Picard, Sparrow, Abraham, Aloui, Atesoglu,
  Attore, Bass{\"u}ll{\"u}, Bey, Garzuglia, Garc{\'\i}a-Montero, Groot, Guerin,
  Laestadius, Lowe, Mamane, Marchi, Patterson, Rezende, Ricci, Salcedo, Diaz,
  Stolle, Surappaeva \& Castro}]{Bastin2017}
Bastin, J.F., Berrahmouni, N., Grainger, A., Maniatis, D., Mollicone, D.,
  Moore, R., Patriarca, C., Picard, N., Sparrow, B., Abraham, E.M., Aloui, K.,
  Atesoglu, A., Attore, F., Bass{\"u}ll{\"u}, {\c C}., Bey, A., Garzuglia, M.,
  Garc{\'\i}a-Montero, L.G., Groot, N., Guerin, G., Laestadius, L., Lowe, A.J.,
  Mamane, B., Marchi, G., Patterson, P., Rezende, M., Ricci, S., Salcedo, I.,
  Diaz, A.S.P., Stolle, F., Surappaeva, V. \& Castro, R. (2017) The extent of
  forest in dryland biomes. \emph{Science} \textbf{356}, 635--638.

\bibitem[{Brinck \emph{et~al.}(2017)Brinck, Fischer, Groeneveld, Lehmann,
  Dantas De~Paula, Pütz, Sexton, Song \& Huth}]{Brinck2017}
Brinck, K., Fischer, R., Groeneveld, J., Lehmann, S., Dantas De~Paula, M.,
  Pütz, S., Sexton, J.O., Song, D. \& Huth, A. (2017) High resolution analysis
  of tropical forest fragmentation and its impact on the global carbon cycle.
  \emph{Nature Communications} \textbf{8}, 14855.

\bibitem[{Broadbent \emph{et~al.}(2008)Broadbent, Asner, Keller, Knapp,
  Oliveira \& Silva}]{Broadbent2008}
Broadbent, E.N., Asner, G.P., Keller, M., Knapp, D.E., Oliveira, P.J. \& Silva,
  J.N. (2008) Forest fragmentation and edge effects from deforestation and
  selective logging in the brazilian amazon. \emph{Biological Conservation}
  \textbf{141}, 1745 -- 1757.

\bibitem[{Brooks \emph{et~al.}(2002)Brooks, Mittermeier, Mittermeier,
  da~Fonseca, Rylands, Konstant, Flick, Pilgrim, Oldfield, Magin \&
  Hilton-Taylor}]{Brooks2002}
Brooks, T.M., Mittermeier, R.A., Mittermeier, C.G., da~Fonseca, G.A.B.,
  Rylands, A.B., Konstant, W.R., Flick, P., Pilgrim, J., Oldfield, S., Magin,
  G. \& Hilton-Taylor, C. (2002) Habitat loss and extinction in the hotspots of
  biodiversity. \emph{Conservation Biology} \textbf{16}, 909--923.

\bibitem[{Burns \emph{et~al.}(2016)Burns, Godfrey, Faina, McGee, Hardt,
  Ranivoharimanana \& Randrianasy}]{Burns2016}
Burns, S.J., Godfrey, L.R., Faina, P., McGee, D., Hardt, B., Ranivoharimanana,
  L. \& Randrianasy, J. (2016) {Rapid human-induced landscape transformation in
  Madagascar at the end of the first millennium of the Common Era}.
  \emph{Quaternary Science Reviews} \textbf{134}, 92 -- 99.

\bibitem[{Cornet(1974)}]{Cornet1974}
Cornet, A. (1974) {Essai de cartographie bioclimatique à Madagascar}. Tech.
  rep., Orstom.

\bibitem[{Cox \emph{et~al.}(2012)Cox, Nelson, Tumonggor, Ricaut \&
  Sudoyo}]{Cox2012}
Cox, M.P., Nelson, M.G., Tumonggor, M.K., Ricaut, F.X. \& Sudoyo, H. (2012) {A
  small cohort of Island Southeast Asian women founded Madagascar}.
  \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{279},
  2761--2768.

\bibitem[{Crottini \emph{et~al.}(2012)Crottini, Madsen, Poux, Strau{\ss},
  Vieites \& Vences}]{Crottini2012}
Crottini, A., Madsen, O., Poux, C., Strau{\ss}, A., Vieites, D.R. \& Vences, M.
  (2012) {Vertebrate time-tree elucidates the biogeographic pattern of a major
  biotic change around the K--T boundary in Madagascar}. \emph{Proceedings of
  the National Academy of Sciences} \textbf{109}, 5358--5363.

\bibitem[{Eklund \emph{et~al.}(2016)Eklund, Blanchet, Nyman, Rocha, Virtanen \&
  Cabeza}]{Eklund2016}
Eklund, J., Blanchet, F.G., Nyman, J., Rocha, R., Virtanen, T. \& Cabeza, M.
  (2016) {Contrasting spatial and temporal trends of protected area
  effectiveness in mitigating deforestation in Madagascar}. \emph{Biological
  Conservation} \textbf{203}, 290 -- 297.

\bibitem[{Freudenberger(2010)}]{Freudenberger2010}
Freudenberger, K. (2010) {Paradise Lost? Lessons from 25 years of USAID
  environment programs in Madagascar}. \emph{International Resources Group,
  Washington DC} .

\bibitem[{Gibson \emph{et~al.}(2013)Gibson, Lynam, Bradshaw, He, Bickford,
  Woodruff, Bumrungsri \& Laurance}]{Gibson2013}
Gibson, L., Lynam, A.J., Bradshaw, C.J., He, F., Bickford, D.P., Woodruff,
  D.S., Bumrungsri, S. \& Laurance, W.F. (2013) Near-complete extinction of
  native small mammal fauna 25 years after forest fragmentation. \emph{Science}
  \textbf{341}, 1508--1510.

\bibitem[{Goodman \& Benstead(2005)}]{Goodman2005}
Goodman, S.M. \& Benstead, J.P. (2005) {Updated estimates of biotic diversity
  and endemism for Madagascar}. \emph{Oryx} \textbf{39}, 73--77.

\bibitem[{Gorenflo \emph{et~al.}(2011)Gorenflo, Corson, Chomitz, Harper,
  Honzák \& {\"O}zler}]{Gorenflo2011}
Gorenflo, L.J., Corson, C., Chomitz, K.M., Harper, G., Honzák, M. \&
  {\"O}zler, B. (2011) \emph{{Exploring the Association Between People and
  Deforestation in Madagascar}}, vol. 1650. Springer Berlin Heidelberg.

\bibitem[{Grinand \emph{et~al.}(2017)Grinand, Le~Maire, Vieilledent,
  Razakamanarivo, Razafimbelo \& Bernoux}]{Grinand2017}
Grinand, C., Le~Maire, G., Vieilledent, G., Razakamanarivo, H., Razafimbelo, T.
  \& Bernoux, M. (2017) {Estimating temporal changes in soil carbon stocks at
  ecoregional scale in Madagascar using remote-sensing}. \emph{International
  Journal of Applied Earth Observation and Geoinformation} \textbf{54}, 1--14.

\bibitem[{Grinand \emph{et~al.}(2013)Grinand, Rakotomalala, Gond, Vaudry,
  Bernoux \& Vieilledent}]{Grinand2013}
Grinand, C., Rakotomalala, F., Gond, V., Vaudry, R., Bernoux, M. \&
  Vieilledent, G. (2013) {Estimating deforestation in tropical humid and dry
  forests in Madagascar from 2000 to 2010 using multi-date Landsat satellite
  images and the Random Forests classifier}. \emph{Remote Sensing of
  Environment} \textbf{139}, 68--80.

\bibitem[{Grouzis \emph{et~al.}(2001)Grouzis, Razanaka, Le~Floc’h \&
  Leprun}]{Grouzis2001}
Grouzis, M., Razanaka, S., Le~Floc’h, E. \& Leprun, J.C. (2001)
  {{\'E}volution de la v{\'e}g{\'e}tation et de quelques param{\`e}tres
  {\'e}daphiques au cours de la phase post-culturale dans la r{\'e}gion
  d’Analabo}. \emph{Soci{\'e}t{\'e}s paysannes, transitions agraires et
  dynamiques {\'e}cologiques dans le Sud-Ouest de Madagascar, Antananarivo,
  IRD/CNRE} pp. 327--337.

\bibitem[{Hansen \emph{et~al.}(2013)Hansen, Potapov, Moore, Hancher,
  Turubanova, Tyukavina, Thau, Stehman, Goetz, Loveland, Kommareddy, Egorov,
  Chini, Justice \& Townshend}]{Hansen2013}
Hansen, M.C., Potapov, P.V., Moore, R., Hancher, M., Turubanova, S.A.,
  Tyukavina, A., Thau, D., Stehman, S.V., Goetz, S.J., Loveland, T.R.,
  Kommareddy, A., Egorov, A., Chini, L., Justice, C.O. \& Townshend, J.R.G.
  (2013) {High-Resolution Global Maps of 21st-Century Forest Cover Change}.
  \emph{Science} \textbf{342}, 850--853.

\bibitem[{Harper \emph{et~al.}(2007)Harper, Steininger, Tucker, Juhn \&
  Hawkins}]{Harper2007}
Harper, G.J., Steininger, M.K., Tucker, C.J., Juhn, D. \& Hawkins, F. (2007)
  {Fifty years of deforestation and forest fragmentation in Madagascar}.
  \emph{Environmental Conservation} \textbf{34}, 325--333.

\bibitem[{Humbert(1927)}]{Humbert1927}
Humbert, H. (1927) {La destruction d'une flore insulaire par le feu. Principaux
  aspects de la végétation à Madagascar}. \emph{Mémoires de l'Académie
  Malgache} \textbf{5}, 1--80.

\bibitem[{Keenan \emph{et~al.}(2015)Keenan, Reams, Achard, de~Freitas, Grainger
  \& Lindquist}]{Keenan2015}
Keenan, R.J., Reams, G.A., Achard, F., de~Freitas, J.V., Grainger, A. \&
  Lindquist, E. (2015) {Dynamics of global forest area: Results from the FAO
  Global Forest Resources Assessment 2015}. \emph{Forest Ecology and
  Management} \textbf{352}, 9 -- 20, changes in Global Forest Resources from
  1990 to 2015.

\bibitem[{Kim \emph{et~al.}(2014)Kim, Sexton, Noojipady, Huang, Anand, Channan,
  Feng \& Townshend}]{Kim2014}
Kim, D.H., Sexton, J.O., Noojipady, P., Huang, C., Anand, A., Channan, S.,
  Feng, M. \& Townshend, J.R. (2014) {Global, Landsat-based forest cover change
  from 1990 to 2000}. \emph{Remote Sensing of Environment} \textbf{155},
  178--193.

\bibitem[{Klein(2002)}]{Klein2002}
Klein, J. (2002) {Deforestation in the Madagascar Highlands -- Established
  `truth' and scientific uncertainty}. \emph{GeoJournal} \textbf{56}, 191--199.

\bibitem[{Kull(2000)}]{Kull2000}
Kull, C.A. (2000) {Deforestation, erosion, and fire: degradation myths in the
  environmental history of Madagascar}. \emph{Environment and History}
  \textbf{6}, 423--450.

\bibitem[{MEFT \emph{et~al.}(2009)}]{MEFT2009}
{MEFT, USAID, and CI} (2009) \emph{{Evolution de la couverture de forêts
  naturelles à Madagascar, 1990-2000-2005}}.

\bibitem[{{Ministère de l'Environnement}(1996)}]{IEFN1996}
{Ministère de l'Environnement} (1996) {IEFN: Inventaire Ecologique Forestier
  National}. Tech. rep., {Ministère de l'Environnement de Madagascar,
  Direction des Eaux et Forêts, DFS Deutsch Forest Service GmbH, Entreprise
  d'études de développement rural "Mamokatra", FTM}.

\bibitem[{Minten \emph{et~al.}(2013)Minten, Sander \& Stifel}]{Minten2013}
Minten, B., Sander, K. \& Stifel, D. (2013) {Forest management and economic
  rents: Evidence from the charcoal trade in Madagascar}. \emph{Energy for
  Sustainable Development} \textbf{17}, 106 -- 115, special Issue on Charcoal.

\bibitem[{Murcia(1995)}]{Murcia1995}
Murcia, C. (1995) Edge effects in fragmented forests: implications for
  conservation. \emph{Trends in Ecology \& Evolution} \textbf{10}, 58 -- 62.

\bibitem[{Neteler \& Mitasova(2008)}]{Neteler2008}
Neteler, M. \& Mitasova, H. (2008) \emph{{Open source GIS: a GRASS GIS
  approach}}. Springer.

\bibitem[{Olander \emph{et~al.}(2008)Olander, Gibbs, Steininger, Swenson \&
  Murray}]{Olander2008}
Olander, L.P., Gibbs, H.K., Steininger, M., Swenson, J.J. \& Murray, B.C.
  (2008) {Reference scenarios for deforestation and forest degradation in
  support of REDD: a review of data and methods}. \emph{Environmental Research
  Letters} \textbf{3}, 025011.

\bibitem[{Olofsson \emph{et~al.}(2014)Olofsson, Foody, Herold, Stehman,
  Woodcock \& Wulder}]{Olofsson2014}
Olofsson, P., Foody, G.M., Herold, M., Stehman, S.V., Woodcock, C.E. \& Wulder,
  M.A. (2014) Good practices for estimating area and assessing accuracy of land
  change. \emph{Remote Sensing of Environment} \textbf{148}, 42 -- 57.

\bibitem[{Olofsson \emph{et~al.}(2013)Olofsson, Foody, Stehman \&
  Woodcock}]{Olofsson2013}
Olofsson, P., Foody, G.M., Stehman, S.V. \& Woodcock, C.E. (2013) Making better
  use of accuracy data in land change studies: Estimating accuracy and area and
  quantifying uncertainty using stratified estimation. \emph{Remote Sensing of
  Environment} \textbf{129}, 122 -- 131.

\bibitem[{ONE \emph{et~al.}(2013)}]{ONE2013}
{ONE, DGF, FTM, MNP, and CI} (2013) \emph{{Evolution de la couverture de
  forêts naturelles à Madagascar 2005-2010}}. \url{https://www.pnae.mg/couverture-de-forets-naturelles-2005-2010}

\bibitem[{ONE \emph{et~al.}(2015)}]{ONE2015}
{ONE, DGF, MNP, WCS, and Etc Terra} (2015) \emph{{Changement de la couverture
  de forêts naturelles à Madagascar, 2005-2010-2013}}. \url{https://www.pnae.mg/couverture-de-forets-naturelles-2005-2010-2013}

\bibitem[{Pearson \& Raxworthy(2009)}]{Pearson2009}
Pearson, R.G. \& Raxworthy, C.J. (2009) {The evolution of local endemism in
  Madagascar: watershed versus climatic gradient hypotheses evaluated by null
  biogeographic models}. \emph{Evolution} \textbf{63}, 959--967.

\bibitem[{Pekel \emph{et~al.}(2016)Pekel, Cottam, Gorelick \&
  Belward}]{Pekel2016}
Pekel, J.F., Cottam, A., Gorelick, N. \& Belward, A.S. (2016) {High-resolution
  mapping of global surface water and its long-term changes}. \emph{Nature}
  \textbf{540}, 418--422.

\bibitem[{Perrier~de La~B{\^a}thie(1921)}]{Perrier1921}
Perrier~de La~B{\^a}thie, H. (1921) \emph{{La v{\'e}g{\'e}tation malgache}},
  vol.~23. Mus{\'e}e Colonial.

\bibitem[{Ploch \& Cook(2012)}]{Ploch2012}
Ploch, L. \& Cook, N. (2012) {Madagascar's Political Crisis}.

\bibitem[{Potapov \emph{et~al.}(2017)Potapov, Hansen, Laestadius, Turubanova,
  Yaroshenko, Thies, Smith, Zhuravleva, Komarova, Minnemeyer \&
  Esipova}]{Potapov2017}
Potapov, P., Hansen, M.C., Laestadius, L., Turubanova, S., Yaroshenko, A.,
  Thies, C., Smith, W., Zhuravleva, I., Komarova, A., Minnemeyer, S. \&
  Esipova, E. (2017) {The last frontiers of wilderness: Tracking loss of intact
  forest landscapes from 2000 to 2013}. \emph{Science Advances} \textbf{3}.

\bibitem[{Puyravaud(2003)}]{Puyravaud2003}
Puyravaud, J.P. (2003) Standardizing the calculation of the annual rate of
  deforestation. \emph{Forest Ecology and Management} \textbf{177}, 593--596.

\bibitem[{Rakotomala \emph{et~al.}(2015)Rakotomala, Rabenandrasana,
  Andriambahiny, Rajaonson, Andriamalala, Burren, Rakotoarijaona, Parany,
  Vaudry, Rakotoniaina, Ranaivosoa, Rahagalala, Randrianary \&
  Grinand}]{Rakotomalala2015}
Rakotomala, F., Rabenandrasana, J., Andriambahiny, J., Rajaonson, R.,
  Andriamalala, F., Burren, C., Rakotoarijaona, J., Parany, B., Vaudry, R.,
  Rakotoniaina, S., Ranaivosoa, R., Rahagalala, P., Randrianary, T. \& Grinand,
  C. (2015) {Estimation de la d{\'e}forestation des for{\^e}ts humides {\`a}
  Madagascar entre 2005, 2010 et 2013: combinaison multi-date d'images LANDSAT,
  utilisation de l'algorithme Random Forest et proc{\'e}dure de validation}.
  \emph{Revue Fran{\c{c}}aise de Photogramm{\'e}trie et de
  T{\'e}l{\'e}d{\'e}tection} pp. 11--23.

\bibitem[{Riitters \emph{et~al.}(2000)Riitters, Wickham, O'Neill, Jones \&
  Smith}]{Riitters2000}
Riitters, K., Wickham, J., O'Neill, R., Jones, B. \& Smith, E. (2000)
  Global-scale patterns of forest fragmentation. \emph{Conservation Ecology}
  \textbf{4}, 3.

\bibitem[{Saatchi \emph{et~al.}(2011)Saatchi, Harris, Brown, Lefsky, Mitchard,
  Salas, Zutta, Buermann, Lewis, Hagen, Petrova, White, Silman \&
  Morel}]{Saatchi2011}
Saatchi, S.S., Harris, N.L., Brown, S., Lefsky, M., Mitchard, E.T.A., Salas,
  W., Zutta, B.R., Buermann, W., Lewis, S.L., Hagen, S., Petrova, S., White,
  L., Silman, M. \& Morel, A. (2011) Benchmark map of forest carbon stocks in
  tropical regions across three continents. \emph{Proceedings of the National
  Academy of Sciences} \textbf{108}, 9899--9904.

\bibitem[{Saunders \emph{et~al.}(1991)Saunders, Hobbs \&
  Margules}]{Saunders1991}
Saunders, D.A., Hobbs, R.J. \& Margules, C.R. (1991) {Biological Consequences
  of Ecosystem Fragmentation: A Review}. \emph{Conservation Biology}
  \textbf{5}, 18--32.

\bibitem[{Scales(2011)}]{Scales2011}
Scales, I.R. (2011) {Farming at the Forest Frontier: Land Use and Landscape
  Change in Western Madagascar, 1896-2005}. \emph{Environment and History}
  \textbf{17}, 499--524.

\bibitem[{Smith \emph{et~al.}(2003)Smith, Muir, Walpole, Balmford \&
  Leader-Williams}]{Smith2003}
Smith, R.J., Muir, R.D.J., Walpole, M.J., Balmford, A. \& Leader-Williams, N.
  (2003) Governance and the loss of biodiversity. \emph{Nature} \textbf{426},
  67--70.

\bibitem[{Tidd \emph{et~al.}(2001)Tidd, Pinder \& Ferguson}]{Tidd2001}
Tidd, S.T., Pinder, J. \& Ferguson, G.W. (2001) {Deforestation and habitat loss
  for the Malagasy flat-tailed tortoise from 1963 through 1993}.
  \emph{Chelonian Conservation and Biology} \textbf{4}, 59--65.

\bibitem[{Tropek \emph{et~al.}(2014)Tropek, Sedl{\'a}{\v c}ek, Beck, Keil,
  Musilov{\'a}, {\v S}{\'\i}mov{\'a} \& Storch}]{Tropek2014}
Tropek, R., Sedl{\'a}{\v c}ek, O., Beck, J., Keil, P., Musilov{\'a}, Z., {\v
  S}{\'\i}mov{\'a}, I. \& Storch, D. (2014) {Comment on "High-resolution global
  maps of 21st-century forest cover change"}. \emph{Science} \textbf{344},
  981--981.

\bibitem[{Tyukavina \emph{et~al.}(2015)Tyukavina, Baccini, Hansen, Potapov,
  Stehman, Houghton, Krylov, Turubanova \& Goetz}]{Tyukavina2015}
Tyukavina, A., Baccini, A., Hansen, M.C., Potapov, P.V., Stehman, S.V.,
  Houghton, R.A., Krylov, A.M., Turubanova, S. \& Goetz, S.J. (2015)
  Aboveground carbon loss in natural and managed tropical forests from 2000 to
  2012. \emph{Environmental Research Letters} \textbf{10}, 074002.

\bibitem[{Tyukavina \emph{et~al.}(2017)Tyukavina, Hansen, Potapov, Stehman,
  Smith-Rodriguez, Okpa \& Aguilar}]{Tyukavina2017}
Tyukavina, A., Hansen, M.C., Potapov, P.V., Stehman, S.V., Smith-Rodriguez, K.,
  Okpa, C. \& Aguilar, R. (2017) {Types and rates of forest disturbance in
  Brazilian Legal Amazon, 2000{\textendash}2013}. \emph{Science Advances}
  \textbf{3}.

\bibitem[{{United Nations}(2015)}]{UN2015}
{United Nations} (2015) \emph{{World Population Prospects: The 2015 Revision,
  Key Findings and Advance Tables. Working Paper No. ESA/P/WP.241.}}

\bibitem[{Verhegghen \emph{et~al.}(2016)Verhegghen, Eva, Desclée \&
  Achard}]{Verhegghen2016}
Verhegghen, A., Eva, H., Desclée, B. \& Achard, F. (2016) {Review and
  Combination of Recent Remote Sensing Based Products for Forest Cover Change
  Assessments in Cameroon}. \emph{International Forestry Review} \textbf{18},
  14--25.

\bibitem[{Vieilledent \emph{et~al.}(2016)Vieilledent, Gardi, Grinand, Burren,
  Andriamanjato, Camara, Gardner, Glass, Rasolohery, Rakoto~Ratsimba, Gond \&
  Rakotoarijaona}]{Vieilledent2016}
Vieilledent, G., Gardi, O., Grinand, C., Burren, C., Andriamanjato, M., Camara,
  C., Gardner, C.J., Glass, L., Rasolohery, A., Rakoto~Ratsimba, H., Gond, V.
  \& Rakotoarijaona, J.R. (2016) {Bioclimatic envelope models predict a
  decrease in tropical forest carbon stocks with climate change in Madagascar}.
  \emph{Journal of Ecology} \textbf{104}, 703--715.

\bibitem[{Vieilledent \emph{et~al.}(2013)Vieilledent, Grinand \&
  Vaudry}]{Vieilledent2013}
Vieilledent, G., Grinand, C. \& Vaudry, R. (2013) {Forecasting deforestation
  and carbon emissions in tropical developing countries facing demographic
  expansion: a case study in Madagascar}. \emph{Ecology and Evolution}
  \textbf{3}, 1702--1716.

\bibitem[{Virah-Sawmy(2009)}]{Virah-Sawmy2009}
Virah-Sawmy, M. (2009) {Ecosystem management in Madagascar during global
  change}. \emph{Conservation Letters} \textbf{2}, 163--170.

\bibitem[{Vorontsova \emph{et~al.}(2016)Vorontsova, Besnard, Forest, Malakasi,
  Moat, Clayton, Ficinski, Savva, Nanjarisoa, Razanatsoa, Randriatsara, Kimeu,
  Luke, Kayombo \& Linder}]{Vorontsova2017}
Vorontsova, M.S., Besnard, G., Forest, F., Malakasi, P., Moat, J., Clayton,
  W.D., Ficinski, P., Savva, G.M., Nanjarisoa, O.P., Razanatsoa, J.,
  Randriatsara, F.O., Kimeu, J.M., Luke, W.R.Q., Kayombo, C. \& Linder, H.P.
  (2016) {Madagascar's grasses and grasslands: anthropogenic or natural?}
  \emph{Proceedings of the Royal Society of London B: Biological Sciences}
  \textbf{283}.

\end{thebibliography}

@@

\vspace*{\stretch{1}}
<<comp_forest, results="asis">>=
# Import and format
fcc.comp <- read.table(file="tabs/fcc_comp.txt", sep=" ", header=TRUE)
tab.2 <- fcc.comp
tab.2 <- tab.2[,c(2,1,3:10)]
tab.2[,c(3:10)] <- round(tab.2[,c(3:10)]/1000)
tab.2$ForestType <- c("Total",rep("",3),"Moist",rep(" ",3),"Dry",rep(" ",3),"Spiny",rep(" ",3),"Mangroves",rep(" ",3))
col.names <- c("Forest type","Source","1953","1973","1990","2000","2005","2010","2013","2014")
# Caption
tabcap2 <- "\\textbf{Comparing Madagascar forest cover estimates with
      previous studies on the period 1953-2014}. We compared our
    estimates of forest cover with the estimates from three previous
    studies \\citep{Harper2007, MEFT2009, ONE2015}. Areas are provided
    in thousands of hectares (Kha). We obtained a Pearson's
    correlation coefficient of 0.99 between our forest cover estimates
    and forest cover estimates from previous studies. The increase in
    mangrove and spiny forest covers from \\emph{c.} 1953 to \\emph{c.}
    1973 in \\citet{Harper2007} and our study is most probably due to
    differences in forest definition and mapping methods between the
    1953 aerial-photography derived map and the 1973 Landsat image
    derived map."
# Kable
knitr::kable(tab.2, col.names=col.names, align=c("l","l",rep("r",8)), format.args=list(big.mark=","), 
             booktabs=TRUE, format="latex", caption=tabcap2, linesep="") %>% 
  kable_styling(latex_options=c("striped","hold_position","scale_down"))
@
\vspace*{\stretch{1}}

>>>>

\documentclass[a4paper, 12pt, leqno]{article} %leqno: numéro d'équation à gauche
\pagenumbering{arabic} % choose how to number the pages
\usepackage{a4wide}
\usepackage[utf8]{inputenc} % accents interprétés
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage[hmargin=2cm, vmargin = 2cm, noheadfoot]{geometry} %% Pour gérer le format des pages
%\usepackage{layout} %% Pour avoir la longueur des marges
\usepackage[round,sort]{natbib} %% Natbib is a popular style for formatting references.
\usepackage[nottoc,numbib]{tocbibind} %% Referecnes as section
%\usepackage{multibib}
%\newcites{secnm}{Bibliographie} 
%\usepackage{verbatim} % for multiline comments
\usepackage{amssymb} %symbole de maths
\usepackage{amsmath} %idem
%\usepackage{stmaryrd} %% Symbole flèche à l'envers
%\usepackage{amsfonts}
\usepackage[english]{babel} %% Les titres en anglais
\usepackage{array} %% Pour centrer verticalement le contenu d'un tableau, entre autres...
\setcounter{secnumdepth}{4} %% Profondeur des sections, subsections
\usepackage{setspace} %% Gère l'interligne: singlespacing, doublespacing
\usepackage{booktabs}
%\singlespacing
\usepackage{longtable}
\usepackage[table]{xcolor}
\setlength{\LTleft}{-5cm plus 1 fill}
\setlength{\LTright}{-5cm plus 1 fill}
\usepackage[colorlinks=true,citecolor=blue]{hyperref} %% Gère les hyperliens
\usepackage{lineno} %% Numérotation des lignes
%\linenumbers
\newcommand{\logit}{\text{logit}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\p}{\text{p}}
\newcommand{\R}{\textnormal{\sffamily\bfseries R}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

@@

\title{Combining global tree cover loss data with historical national
  forest cover maps to look at six decades of deforestation and forest
  fragmentation in Madagascar}
\author{}
\date{}

@@

\bibliographystyle{bib/besjournals}
\bibliography{bib/biblio}

@@

\vspace*{\stretch{1}}
<<comp_forest, results="asis">>=
# Import and format
fcc.comp <- read.table(file="tabs/fcc_comp.txt", sep=" ", header=TRUE)
tab.2 <- fcc.comp
tab.2 <- tab.2[,c(2,1,3:10)]
tab.2[,c(3:10)] <- round(tab.2[,c(3:10)]/1000)
tab.2$ForestType <- c("Total",rep("",3),"Moist",rep(" ",3),"Dry",rep(" ",3),"Spiny",rep(" ",3),"Mangroves",rep(" ",3))
col.names <- c("Forest type","Source","1953","1973","1990","2000","2005","2010","2013","2014")
# Caption
tabcap2 <- "\\textbf{Comparing Madagascar forest cover estimates with
      previous studies on the period 1953-2014}. We compared our
    estimates of forest cover with the estimates from three previous
    studies \\citep{Harper2007, MEFT2009, ONE2015}. Areas are provided
    in thousands of hectares (Kha). We obtained a Pearson's
    correlation coefficient of 0.99 between our forest cover estimates
    and forest cover estimates from previous studies. The increase in
    mangrove and spiny forest covers from \\emph{c.} 1953 to \\emph{c.}
    1973 in \\citet{Harper2007} and our study is most probably due to
    differences in forest definition and mapping methods between the
    1953 aerial-photography derived map and the 1973 Landsat image
    derived map."
# Kable
knitr::kable(tab.2, col.names=col.names, align=c("l","l",rep("r",8)), format.args=list(big.mark=","), 
             booktabs=TRUE, format="latex", caption=tabcap2, linesep=c("","","","\\addlinespace")) %>% 
  kable_styling(latex_options=c("striped","hold_position","scale_down"))
@
\vspace*{\stretch{1}}
